Verifying Spatial Properties of Stencil Computations

### 2016-11-15 paper.tex
some of the evaluation results, rough rough draft

@@

% Number of stencils (tickAssign) / number of loops
% Percentage of a code base that is taken up by stencils

@@

@@

% 1. How may are just reflexive and how many some reflexive

% 2. Break down of "interesting specifications" (contain more than
% just reflexive)
%   - Single-action, histogram on depths
%   - Single-action + irreflexives, histogram on depths
%   - Bounded specs (how many lower, upper, or both)
%   - Multi-action combined only by *
%   - Multi-action combined also by +, histogram of tree depths

>>>>

We have processed nearly one million lines of Fortran code using our
CamFort tool and examined the output to try and determine how useful
and applicable it may be. The body of Fortran code is collected from
many computational science projects for which we believe our tool will
be potentially helpful.

@@

%    numStencilSpecs: 60525
% 4338 files, linesTotal: 1357377, linesParsed: 959427
% Number of stencils (tickAssign) / number of loops
% Percentage of a code base that is taken up by stencils

Out of 1.35 million lines of code that we fed into our program, and
the 959,427 lines that we were able to parse, we identified 60,525
cases that fit our criteria for stencil specification.

@@

    % tickAssign: 97439
    % tickAssignSuccess: 29402 % <- number of times tickAssign is accompanied by a successful stencil inference
                               % counts only by +1 each time that tickAssign finds a stencil

In the analysed body of code we found that we were able to deduce
some form of stencil specification from approximately 30\% of the
potential stencils examined.

@@

% 1. How may are just reflexive and how many some reflexive
% justReflexive: 55504
% someReflexive: 15823

55,504 specifications involved only reflexive regions, of which 15,823
only had specifications for some of the dimensions, while 39,681 were
reflexive on all dimensions.

% (/ 55504.0 60525) = 91.7%
% (/ 15823.0 60525) = 26.1%
% 91.7\% of the specifications involved only reflexive regions. 26.1\%

% 2. Break down of "interesting specifications" (contain more than
% just reflexive)
%   - Single-action, histogram on depths
%   - Single-action + irreflexives, histogram on depths
%   - Bounded specs (how many lower, upper, or both)

Bounded specifications were fairly unusual, with only 157
\texttt{atMost} and 36 \texttt{atLeast}, the latter of which were
always also bounded on both sides.
    % atLeast: 36
    % atMost: 157
    % boundedBoth: 36

%   - Multi-action combined only by *
%   - Multi-action combined also by +, histogram of tree depths
